Binning Strategies and Related Loss for Large Data

### 2015-02-25 Paper.Rnw
Changes made to generally binning description

\section{Binning \hh{Algorithms}}
\hh{XXX Motivation first - starting with the limitiations too  negative.}

@@

Binning is a two-step procedure: we first assign each \hh{observation} $(x, y)$ to a bin center $(x^\ast,y^\ast)$, and in a second step we find the frequency of each bin center \hh{``frequency of each bin center" ... that needs a few more words, because there is only one bin center. But what you mean is that each observation assigned to the bin center now counts as one value for the bin center. XXX The next sentence explains that, so combine the two sentences a bit more}, resulting in  triples  of the form $(x^\ast, y^\ast, c)$, where $c$ is the number of all observations assigned to bin center $(x^\ast,y^\ast)$.

>>>>

\section{Binning Algorithms}
\hh{XXX Motivation first - starting with the limitiations too  negative.}

@@

\ktm{Binning is a two-step procedure: we first assign each observation $(x, y)$ to a bin center $(x^\ast,y^\ast)$, and in a second step we count the number of observations assigned to each unique bin center; resulting in  triples  of the form $(x^\ast, y^\ast, c)$, where $c$ is the number of all observations assigned to bin center $(x^\ast,y^\ast)$.}
